---
title: "Homework2"
output: html_document
---
Challenge: the data set rairuoho provides growth data for 8 days in different treatments. Reformat the table in order to have the day as a variable with 6 levels together with another variable called length. You may use another famous package for data manipulation tidyr and the function gather(). Current variables are given as:


- day3 to day8: mean length of the grass at the given day

- germinate: no. of germinated seeds

- bed: where the grass was growing, 4 levels: thin (mould1), thick (mould2) mould, thin (paper4) and thick (paper8) paper

- treatement: watering scheme, 2 levels: either pure water or water with nutrients

- spatial1: vertical location of the plot

- spatial2: horizontal location of the plot

extra variable row and column can be removed

```{r}
library(tidyr)
rairuoho<-read.table("C:/Users/Mariana Reyes/Documents/Rclass/GitAndR/rairuoho.txt",header=T, sep="\t", dec=".")
head(rairuoho)

```



```{r}

colnames(rairuoho) <- c('3','4','5','6','7','8','Germinate','Bed','Treatment','Spatial 1', 'Spatial 2', 'row', 'column')
rairuoho

```

```{r}
rairuoho <- subset(rairuoho, select = -c (row,column))

rairuoho1 <- gather(rairuoho, "Days", "Length", 1:6)

rairuoho1
```
